Transcriptomic Analysis for Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-06-28 Cover_letter_JPM.tex
Updates from Overleaf

May 16, 2021

@@

Enclosed, please find our revised manuscript (jpm-1174473) entitled "Transcriptomic Analysis of Expressions of Biomarkers and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma" by Chi et al., which we wish to be considered for publishing as a research article in Journal of Personalized Medicine. We appreciate your time serving as the editor handling this manuscript and thank the reviewers for their critical comments and suggestions on our manuscript.

@@

%{%
Reviewer 1: % {2-4}
"Please shortly explain the TCGA database in the Introduction and summarize the advantages of its use."\\
We re-wrote the Introduction in detail according to the suggestion by reviewer \#2. %(comment No 2-4).
%}

Reviewer 2: % {3-1}
"Are the conclusions supported by the results?
Only computer computing in this research to support 20 candidate biomarkers, ... are all heavily associated with the prognosis of OS.
There is little information provided. The authors should provide more evidence to support this article."\\
We provide more evidence by additional analysis of TCGA and GEO databases. Moreover, we reviewed literature that supports the prognostic impact of these candidate genes.
According to the suggestion by reviewer \#3,
we re-wrote the Discussion with additional information, and
%}
%{% Answer_3-1_USP10.pdf, Answer_2-1.pdf
%According to the reviewers' comments, we 
added new supplementary Figure S1, S2, and S3 %, S2, S3, and Table S2. We also replaced Figure 3D and 4A with high magnitude images from the same slides. We transferred the original Figure 2 into supplementary Figure S1 
to provide more evidence from the significant literature review.
%}

According to the editor's comments, we have the manuscript checked for English grammar. %
We wish our revised manuscript could be satisfied and accepted for publication in JPM. Thanks very much for the kind helps and the reviewers' critical comments.
%\\[0.4cm]
Kind regards,

@@

\begin{MyColorPar}{blue}
Answer
%(OK)
We appreciate the reviewer for the critical comments and thanks for the agreement with our analysis using the TCGA cohort.

The manuscript posted in the preprint server, ResearchSqaure, is our first version (2020/09/28) of current manuscript. 
Since previous reviewer's suggestion, we made a major revision on the followings:
1) suggested candidates of biomarker has been modified  by additional validation using an independent patient cohort (GSE2837).
We also reviewed literature that supports the prognostic impact of these candidate genes. The resulting Figure 4, Table 3 and Table 4 is different between the two manuscripts.
2) Since that revision, we added holistic cancer care in the discussion section (please see Answer 1-2).% \ref{page:1-2}).

@@

\begin{MyColorPar}{blue}
Answer
%(OK)
After morning meditation in a wonderful day of February 2021,, the first author (Dr. Chi) has raised this idea then wrote it in discussion section with comprehensive references. Dr. Chi want to express that "Stress should also be a kind of biomarker included in the future HNSCC study".
We appreciate the reviewer for the agreement about mindfulness meditation and holistic cancer care. We will brief this issue and move rest of it in the other manuscript.

@@

\begin{MyColorPar}{red}
"%discussion: the third limitation
There are eighty-one physical, pathological and social conditions derived from participants available for survival modeling in the TCGA, % since it has comprehensive clinical features, 
such as age, gender, residual tumor, vital status, days-to-last-followup, cancer stage, smoking duration, exposure to alcohol, asbestos, radioactive radon. 
However, the TCGA did not collect other features related to holistic care.
% Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage; emotional 情緒(心)
Going for holistic cancer care\cite{Mehta2019}\cite{Iftikhar2021}, spiritual and emotional condition is equally essential comparing with physical and social status (see Figure 5).%\ref{fig:figure5}).
Psychosocial stress is associated with cancer incidence\cite{Lutgendorf2010}\cite{Powell2013}\cite{Iftikhar2021}, metastasis\cite{Lutgendorf2010}\cite{Moreno-Smith2010}\cite{Du2020}\cite{Xu2021}, and poor survival\cite{Chida2008}.
These impacts might be mediated through the hypothalamic-pituitary-adrenal (HPA) axis\cite{Hsiao2012}.
Holistic healthcare providers will engage his/her patients with eye-to-eye contact in terms of mind-to-mind connection. Their empathy, sympathy, and compassion is induced by the suffering of patients from those diseases. They will try to treat patients by prescribing medicine (and "themselves") or performing surgery.
Thus, the healing resilience of patients will be induced by unconditional positive regard. % of healing.
The patients will trust those who take care of them and have the confidence to increase the capacity to recover from diseases through a mind-brain-body connection manner (see Figure 5).%\ref{fig:figure5}).
"

@@

%There is so many thing we could find during the data mining from so many 20500 protein-coding genes.
We performed the FDR correction applied on the Kaplan-Meier \textit{P} values of cutoff finding procedure, then Bonferroni adjustment of those \textit{P} values for candidate selection.
%\begin{MyColorPar}{red}
%\end{MyColorPar}
% and FDR (done; ok)
We modified the last paragraph of "Cutoff Finder Core Engine" in the Material and Methods section.
%Figure 1, Table 1, 2 correction: Kaplan-Meier FDR correction
%***The caption of Figure 1 and Table 1 has description about 1) FDR correction of Kaplan-Meier \textit{P} values during Cutoff finding; and 2) Bonferroni correction of Kaplan-Meier \textit{P} values after Cox modeling for candidate selection.
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it is shown here in the following paragraph.
\\[0.3cm]

@@

% (stored at HNSCC_survivalAnalysis_marginS_[gene].Rda; file20500_list.txt)
The \acrfull{fdr} ($< 0.05$) correction\cite{Benjamini1995a} has been be applied and shows which genes should be retained for further univariate and multivariate analysis.
% of Cox modeling
It is ensure the control of type I error of multiple test \textit{P} values during our cutoff finding procedure.
Then Bonferroni adjustment of those \textit{P} values has been used for candidate selection.
\end{MyColorPar}

@@

%
\begin{MyColorPar}{blue}
Answer
%(OK)
We appreciate the reviewer for the critical comment.
We changed title as "Transcriptomic Analysis of Expressions of Biomarkers and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma", and abstract; we also changed the tone in our manuscript to focus on the identified biomarkers in the head and neck squamous cell carcinoma.
There is more evidence to validate them (please see Answer 2-3).

@@

@@

We modified the paragraphs in the "Material and Methods" section and "Results" section for the analysis of GSE65858.
We also described "the \textit{P} values are affected by the sample size" in the Discussion section.
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it is shown here in the following paragraph.
\\[0.3cm]

@@

[materials and methods]\\
%RefSeq Release 38 (November 7, 2009) 
%[Dataset]
The Gene Expression Omnibus (GEO) database, founded by \acrfull{ncbi}, is a public repository supporting MIAME-compliant data submissions of microarray and sequence-based experiments.
R package of GEOquery\cite{Sean2007} was used to
download RNA-Seq dataset (in SOFT or MINiML format) of a HNSCC cohort, GSE65858, from the GEO database (available at https://www.ncbi.nlm.nih.gov/geo/geo2r/?\\acc=GSE65858). 
GSE65858\cite{Wichmann2015} has OS event, RFS event and survival time.
There are 270 HNSCC participants involved in this cohort.
%The number of genes (or probes of RNA-Seq in platform GPL10558, Illumina HumanHT-12 V4.0 expression beadchip) is 30,330.
%n=270 n= 273 = ?? + 168(alive) + 88(dead) = 256
The expression data was generated using the platform GPL10558 (Illumina HumanHT-12 v4.0 Expression BeadChip), which targets on more than 30,330 annotated genes (47,000 probes, derived from the \acrshort{ncbi} Reference Sequence, release 38 on November 7, 2009). % (RefSeq) 
GSE65858 is a dataset for candidate selection in our workflow.
We have also performed Kaplan-Meier and Cox survival analyses, under the cutoff of each gene expression at their median value.\\

[Results]\\
TCGA HNSCC cohort has been applied for exploration of the biomarker candidate
Total 9416 genes has %\acrshort{fdr}-
unadjusted \textit{P} value less than 0.05.
The 967 genes were kept by criteria of uncorrected \textit{P} value (below 0.05) and \acrfull{hr} (greater than 1.8 or less than 0.6).
%The 10 genes, named as DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1, are significantly associated with the poor prognosis of overall survival (OS). 
%The other ten genes are over-expressed in the better survival group (with hazard ratio $<=0.6$), named as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB.
Furthermore, CAMK2N1, IL19, FCGBP and the other 17 genes (DKK1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, ZNF557, ZNF266, MYO1H, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB) have significant FDR-adjusted \textit{P} values ($<0.0003$) in Kaplan-Meier estimate, and greater hazard ratio (HR) ($> 1.8$ or $< 0.6$) in Cox's model (please see Figure \ref{fig:hazards3}; $log_{10}(0.0003)=-3.5$).
%During our exploration phase with TCGA cohort, the 20 genes, listed
%six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
%four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are good guy.
%}
%in Figure \ref{fig:hazards3}, have FDR-adjusted \textit{P} values ($<0.001$) in Kaplan-Meier estimate, and survival impact on HR ($> 1.8$ or $< 0.6$) in Cox's model.

% [2021/06/13-17] GSE65858
%CAMK2N1, IL19, and FCGBP is validated by
%candidate_fdr100
%PvalueTex consensus with GSE2837 to yield 3 candidates
In the study of GSE65858 cohort with median cutoffs, CAMK2N1, IL19, and FCGBP (3 of the 20 genes), keep ahead of the curve by their FDR-corrected \textit{P} value ($< 0.05$), and Cox'HR ($>1.8$ or $<0.65$) (please see Table \ref{tab:table_top3_GSE65858} listed below,
% (ok) (FDR KM \textit{P} value) <= # only MSMB KM FDR-adjusted P value = 0.002 
% Consensus 3 genes in Kaplan-Meier survival and Cox's model (dataset: GSE65858)
%Gene.Symbol KM.Pvalue   FDR.KMpvalue    uni_HR  FDR.Pvalue(in TCGA)
%CAMK2N1 0.00687 0.03782500  1.814   1.628308e-05
%FCGBP   0.01020 0.03886709  0.573   4.827833e-05
%IL19    0.03390   0.04738901    0.630   6.543871e-06
%IL19    0.00269  0.03068073 0.630  6.543871e-06
%candidate_fdr100
and also see Figure \ref{fig:hazards534}).
However, the significance of the other 17 genes is replaced by genes such as DUSP6, MSMB, and RBM11 (please see Figure \ref{fig:hazards534}).
%This GSE65858 cohort has been applied for selection to generate our candidate genes: \textcolor{red}{CAMK2N1}, \textcolor{red}{IL19} (two probes), and , \textcolor{red}{FCGBP}.
Moreover, there are 22 genes, which have greater hazard ratio ($> 1.8$ or $< 0.6$) in GSE65858 cohort (Figure \ref{fig:hazards534}), drop their hazard ratio between 0.6 and 1.5 in the study of TCGA HNSCC (Figure \ref{fig:hazards3}).
Thus, there is a consensus between the TCGA and GSE65858 cohorts that CAMK2N1, IL19 (two probes), and FCGBP are significant candidates for the HNSCC biomarker.
%The consensus between the TCGA and GSE65858 cohorts in Kaplan-Meier survival and Cox's model

[Discussion]\\
%[more in the discussion section]
1) \\% (ok)
Statistical significance (\textit{P} value) is affected by both sample size, error, effect size (substantive significance)\cite{Sullivan2012}\cite{Thiese2016}, and cutoff. 
The effect size is the magnitude of the difference (or relationship) among comparing groups.
%A \textit{P} value is a tool to help interpret findings from biomedical research.
%In reporting and interpreting studies, both 
%the substantive significance (effect size) and statistical significance (P value) are essential results to be reported.
While statistical significance can inform the researcher whether an effect exists, 
the \textit{P} value will not directly tell the effect size.
%The effect size is the main finding of a quantitative study.
%Statistical significance depends upon both sample size and effect size. 
The effect size is independent of the sample size\cite{Sullivan2012}.

%When we increase the sample size, the standard error decrease
%, or increase the difference between the sample statistic and hypothesized parameter, the p value decreases, thus making it more likely that we reject the null hypothesis.
The larger the sample the more likely a difference to be noticed (i.e. \textit{P} value $< 0.05$), due to the decrease of the standard error\cite{Sullivan2012}.
However, the small effect size (non-zero) is often meaningless (substantive insignificance).
%With a sufficiently large sample, a statistical test will always reveal a significant difference, unless the effect size is exactly zero.
%, that is, when the effect size is exactly zero; 
%yet very small differences, even if significant, are often meaningless. 
%Thus, reporting only the significant P value for an analysis is not adequate for readers to fully understand the results.
%If the magnitude of effect is small and clinically unimportant, the p-value can be "significant" if the sample size is large.
Conversely, an effect size can be large, but fail to get statistical significance if the sample size is small. 
%In this scenario, the \textit{P} value tells the effect does not exist.

The \textit{P} value could be also impacted by error, which includes:
\begin{outline}
\1 A random error, defined as variability in data, is not considered a bias but rather occurs random across the entire study population and can distort the measurement process (e.x. RNA-Seq experiments).
The larger sample size could reduce the random error. 
\1 A systematic error is a bias, which includes selection bias, information bias, and confounding.
It could deleteriously impact the statistical significance.
The larger sample size could not affect the systematic error.
\end{outline}
% effect size is large (whatever is true or artificial), the p value is small
Thus, if there is no error in two study groups, and the sample size is the same, the group, which has a larger effect size, will has small \textit{P} value\cite{Thiese2016}.
If a skewed cutoff that split, for example, 425 vs 75 between the two groups, it will also get statistical significance by increasing effect size artificially.
% https://stats.stackexchange.com/questions/162359/how-can-you-have-p-0-0001-with-a-sample-size-of-89-and-a-control-group-of-52
%As you can see, even with only 12 events (fustat = 1) that split 10 vs 2 between the two dummy groups you get a log-rank p-value < 0.0001.
%effect size, sample size, cutoff 影響 p value!

@@

%2) \\
%(ok) % pvalueTex is essential
There is a benefit for using sliding-window cutoff method (avoiding a skewed cutoff) in Kaplan-Meier analysis of TCGA HNSCC cohort at the beginning.
We have compared the results of cutoff at optimal \textit{P} value by sliding-window or just at median of gene expression.
It shows that the number of genes with unadjusted \textit{P} value $<0.05$, which is 6284 vs. 3118, respectively. After FDR-correction, it has reduced as 967 vs. 209, respectively.
% HNSCC_OS_marginS_THREE_pvalue005_noCancerGene
%Result by optimal cutoff: total 9416 plots,
%6284 are raw KM P value < 0.05
%534?? genes are FDR KM P value <0.05
%967 genes which HR is greater than 1.5 or less than 0.5.
%Result by median cutoff: total 20080 genes, 
%3118 are raw KM P value < 0.05; 
%209 genes are FDR KM P value <0.05
The sliding-window cutoff method could catch more potential candidates, which have \textit{P} values far less than $0.001$, for subsequent Cox's modeling.
That is because of proper selected cutoff improving the statistical significance.
Then, these preliminary candidates will have an opportunity to be carefully selected by Bonferroni correction, their effect size (HR), and the other independent cohorts (GSE65858, GSE2837) to prevent the false discovery.

@@

We will explain above mentioned by two examples.
%***NDFIP1  % 給他們一個機會
Reviewing the special cases of gene, such as NDFIP1, DKC1, PNMA5, and NPB,
we have noticed that NDFIP1, with a \textit{P} value of 0.05 at 50\% quantile (median) cutoff, could achieve a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff.
NDFIP1 has the FDR-corrected \textit{P} value as \num[round-precision=3, round-mode=figures,
scientific-notation=true]{0.0001074233} (please see supplementary figure S1, a "W"-shaped \textit{P} value plot). % it is \ref{fig:pvaluePlot_NDFIP1
%Moreover, the gene NDFIP1, one of our 20 preliminary candidates, has a \textit{P} value (around $0.05$) at 50\% quantile cutoff, achieving a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff (please see Figure \ref{fig:pvaluePlot_NDFIP1}, and also in supplementary figure S1).
%After the FDR correction, NDFIP1 still has \textit{P} value of \num[round-precision=3, round-mode=figures, scientific-notation=true]{0.0001074233}.
% the effect size
Then it has been excluded as a candidate by less effect size (HR = 1.33) in GSE65858 cohort, compared with one (HR = 2.027) in TCGA cohort%.
, and the other (HR = 1.42) in GSE2837 cohort.
% (ok) Answer 2-1 加入 discussion
%According to the results of sliding-window cutoff finding, the preliminary biomarkers have FDR-corrected \textit{P} values from \num{1e-4} to 0.04 which have been grouped by cutoffs between 50\% and 70\% quantile (Please see Figure \ref{fig:figure4}; it is also shown in manuscript as updated "Figure 4": top 3 candidate biomarkers, CAMK2N1, IL19, and FCGBP).

@@

Usually, researchers developed in-house workflow of gene expression analysis to find HNSCC biomarkers.

@@

They have a number of genes that are differentially expressed between tumor and normal samples.
It would be useful to show that alteration in gene expression correlates with phenotypes of HNSCC.

@@

The protein-protein interaction (PPI) network was conducted by STRING (availalbe at https://string-db.org).

@@

%%%%%%%%%
\end{MyColorPar}

>>>>

June 30, 2021

@@

Enclosed, please find our revised manuscript (jpm-1174473) entitled "Transcriptomic Analysis for Prognostic Value in Head and Neck Squamous Cell Carcinoma" by Chi et al., which we wish to be considered for publishing as a research article in Journal of Personalized Medicine. We appreciate your time serving as the editor handling this manuscript and thank the reviewers for their critical comments and suggestions on our manuscript.

@@

%{% A SUMMARY
Reviewer 1: % {2-4}
%"Please shortly explain the TCGA database in the Introduction and summarize the advantages of its use."\\
We re-wrote the Introduction in detail according to the suggestion by reviewer \#2.
added new supplementary Figure S1, S2, and S3
Reviewer 2: % {3-1}
%"Are the conclusions supported by the results?
We provide more evidence by additional analysis of TCGA and GEO databases. Moreover, we reviewed literature that supports the prognostic impact of these candidate genes.
%, S2, S3, and Table S2. We also replaced Figure 3D and 4A with high magnitude images from the same slides. We transferred the original Figure 2 into supplementary Figure S1 
%to provide more evidence from the significant literature review.
%}

%According to the editor's comments, we have the manuscript checked for English grammar. %
We wish our revised manuscript could be satisfied and accepted for publication in Journal of Personalized Medicine. 
Thanks very much for the kind helps and the reviewers' critical comments.
%\\[0.4cm]
Kind regards,

@@

\begin{MyColorPar}{blue}
Answer\\
%(OK)
We appreciate the reviewer for the critical comments and thanks for the agreement with our analysis using the TCGA cohort.

The manuscript posted in the preprint server, ResearchSqaure, is our first version (2020/09/28) of current manuscript. 
Since previous reviewer's suggestion, we made a major revision on the followings:
1) suggested candidates of biomarker has been modified  by additional validation using an independent patient cohort (GSE2837).
We also reviewed literature that supports the prognostic impact of these candidate genes. The resulting Figure 4, Table 3 and Table 4 is different between the two manuscripts.
2) Since that revision, we added holistic cancer care in the discussions section (please see Answer 1-2).% \ref{page:1-2}).

@@

\begin{MyColorPar}{blue}
Answer\\
%(OK)
After morning meditation in a wonderful day of February 2021,, the first author (Dr. Chi) has raised this idea then wrote it in discussion section with comprehensive references. Dr. Chi want to express that "Stress should also be a kind of biomarker included in the future HNSCC study".
We appreciate the reviewer for the agreement about mindfulness meditation and holistic cancer care. We will brief this issue and move rest of it in the other manuscript.

@@

\begin{MyColorPar}{red}
" %discussion: the third limitation
There are eighty-one physical, pathological and social conditions derived from participants available for survival modeling in the TCGA, % since it has comprehensive clinical features, 
such as age, gender, residual tumor, vital status, days-to-last-followup, cancer stage, smoking duration, exposure to alcohol, asbestos, radioactive radon. 
However, the TCGA did not collect other features related to holistic care.
% Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage; emotional 情緒(心)
Going for holistic cancer care\cite{Mehta2019}\cite{Iftikhar2021}, spiritual and emotional condition is equally essential comparing with physical and social status (see Figure 5).%\ref{fig:figure5}).
Psychosocial stress is associated with cancer incidence\cite{Lutgendorf2010}\cite{Powell2013}\cite{Iftikhar2021}, metastasis\cite{Lutgendorf2010}\cite{Moreno-Smith2010}\cite{Du2020}\cite{Xu2021}, and poor survival\cite{Chida2008}.
These impacts might be mediated through the hypothalamic-pituitary-adrenal (HPA) axis\cite{Hsiao2012}.
Holistic healthcare providers will engage his/her patients with eye-to-eye contact in terms of mind-to-mind connection. Their empathy, sympathy, and compassion are induced by the suffering of patients from those diseases. They will try to treat patients by prescribing medicine (and "themselves") or performing surgery.
Thus, the healing resilience of patients will be induced by unconditional positive regard. % of healing.
The patients will trust those who take care of them and have the confidence to increase the capacity to recover from diseases through a mind-brain-body connection manner (see Figure 5).%\ref{fig:figure5}).
"

@@

%There is so many thing we could find during the data mining from so many 20500 protein-coding genes.
We performed the FDR correction applied on the Kaplan-Meier \textit{P} values of cutoff finding procedure, then Bonferroni adjustment of those \textit{P} values for candidate selection.
%\begin{MyColorPar}{red}
%\end{MyColorPar}
% and FDR (done; ok)
We modified the last paragraph of "Cutoff Finder Core Engine" in the Materials and Methods section.
%Figure 1, Table 1, 2 correction: Kaplan-Meier FDR correction
%***The caption of Figure 1 and Table 1 has description about 1) FDR correction of Kaplan-Meier \textit{P} values during Cutoff finding; and 2) Bonferroni correction of Kaplan-Meier \textit{P} values after Cox modeling for candidate selection.
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it is shown here in the following paragraph.
\\[0.3cm]

@@

% (stored at HNSCC_survivalAnalysis_marginS_[gene].Rda; file20500_list.txt)
"
The \acrfull{fdr} ($< 0.05$) correction\cite{Benjamini1995a} shows which genes should be retained for subsequent univariate and multivariate analysis.
% of Cox modeling
It ensures the control of type I error of multiple test \textit{P} values during our cutoff finding procedure.
Then Bonferroni adjustment of that \textit{P} values has been used for candidate selection.
"
\end{MyColorPar} % red

@@

%
\begin{MyColorPar}{blue}
Answer
%(OK)
We appreciate the reviewer for the critical comment.
We changed title, "Transcriptomic Analysis for Prognostic Value in Head and Neck Squamous Cell Carcinoma", and abstract; we also changed the tone in our manuscript to focus on the identified biomarkers in the head and neck squamous cell carcinoma.
There is more evidence to validate them (please see Answer 2-3).

@@

%
\begin{MyColorPar}{blue}
Answer\\

@@

We modified the paragraphs in the "Material and Methods" section and "Results" section for the analysis of GSE65858.
We also described "the \textit{P} values are affected by the sample size" in the Discussions section.
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it is shown here in the following paragraph.
\\[0.3cm]

@@

(In the section of Materials and Methods)\\
%RefSeq Release 38 (November 7, 2009) 
%[Dataset]
"
The Gene Expression Omnibus (GEO) database, founded by \acrfull{ncbi}, is a public repository supporting MIAME-compliant data submissions of microarray and sequence-based experiments.
R package of GEOquery\cite{Sean2007} was used to
download RNA-Seq dataset (in SOFT or MINiML format) of a HNSCC cohort, GSE65858, from the GEO database (available at https://www.ncbi.nlm.nih.gov/geo/geo2r/?\\acc=GSE65858). 
GSE65858\cite{Wichmann2015} has OS event, RFS event, and survival time.
There are 270 HNSCC participants involved in this cohort.
%The number of genes (or probes of RNA-Seq in platform GPL10558, Illumina HumanHT-12 V4.0 expression beadchip) is 30,330.
%n=270 n= 273 = ?? + 168(alive) + 88(dead) = 256
The expression data was generated using the platform GPL10558 (Illumina HumanHT-12 v4.0 Expression BeadChip), which targets on more than 30,330 annotated genes (47,000 probes, derived from the \acrshort{ncbi} Reference Sequence, release 38 on Nov 7, 2009). % (RefSeq) 
GSE65858 is a dataset for candidate selection in our workflow.
We have also performed Kaplan-Meier and Cox survival analyses under the cutoff of each gene expression at their median value.\\
"

(In the section of Results)\\
"
TCGA HNSCC cohort has been applied for exploration of the biomarker candidate
Total 9416 genes has %\acrshort{fdr}-
unadjusted \textit{P} value less than 0.05.
The 967 genes were kept by criteria of uncorrected \textit{P} value (below 0.05) and \acrfull{hr} (greater than 1.8 or less than 0.6).
%The ten genes, named DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1, are significantly associated with the poor prognosis of overall survival (OS). 
%The other ten genes are over-expressed in the better survival group (with hazard ratio $<=0.6$), named as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB.
Furthermore, CAMK2N1, IL19, FCGBP and the other 17 genes (DKK1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, ZNF557, ZNF266, MYO1H, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB) have significant FDR-adjusted \textit{P} values ($<0.0003$) in Kaplan-Meier estimate, and greater hazard ratio (HR) ($> 1.8$ or $< 0.6$) in Cox's model (please see Figure \ref{fig:hazards3}; $log_{10}(0.0003)=-3.5$).
%During our exploration phase with TCGA cohort, the 20 genes, listed
%six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
%four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are good guy.
%}
%in Figure \ref{fig:hazards3}, have FDR-adjusted \textit{P} values ($<0.001$) in Kaplan-Meier estimate, and survival impact on HR ($> 1.8$ or $< 0.6$) in Cox's model.

% [2021/06/13-17] GSE65858
%CAMK2N1, IL19, and FCGBP is validated by
%candidate_fdr100
%PvalueTex consensus with GSE2837 to yield 3 candidates
In the study of GSE65858 cohort with median cutoffs, CAMK2N1, IL19, and FCGBP (3 of the 20 genes), keep ahead of the curve by their FDR-corrected \textit{P} value ($< 0.05$), and Cox'HR ($>1.8$ or $<0.65$) (please see Table \ref{tab:table_top3_GSE65858} listed below,
% (ok) (FDR KM \textit{P} value) <= # only MSMB KM FDR-adjusted P value = 0.002 
% Consensus 3 genes in Kaplan-Meier survival and Cox's model (dataset: GSE65858)
%Gene.Symbol KM.Pvalue   FDR.KMpvalue    uni_HR  FDR.Pvalue(in TCGA)
%CAMK2N1 0.00687 0.03782500  1.814   1.628308e-05
%FCGBP   0.01020 0.03886709  0.573   4.827833e-05
%IL19    0.03390   0.04738901    0.630   6.543871e-06
%IL19    0.00269  0.03068073 0.630  6.543871e-06
%candidate_fdr100
and also see Figure \ref{fig:hazards534}).
However, the significance of the other 17 genes are replaced by genes such as DUSP6, MSMB, and RBM11 (please see Figure \ref{fig:hazards534}).
%This GSE65858 cohort has been applied for selection to generate our candidate genes: \textcolor{red}{CAMK2N1}, \textcolor{red}{IL19} (two probes), and , \textcolor{red}{FCGBP}.
Moreover, there are 22 genes, which have greater hazard ratio ($> 1.8$ or $< 0.6$) in GSE65858 cohort (Figure \ref{fig:hazards534}), drop their hazard ratio between 0.6 and 1.5 in the study of TCGA HNSCC (Figure \ref{fig:hazards3}).
Thus, there is a consensus between the TCGA and GSE65858 cohorts that CAMK2N1, IL19 (two probes), and FCGBP are significant candidates for the HNSCC biomarker.
"
%The consensus between the TCGA and GSE65858 cohorts in Kaplan-Meier survival and Cox's model

(In the Discussions section)\\
%[more in the discussion section]
"  % (ok)
Statistical significance (\textit{P} value) is affected by both sample size, error, effect size (substantive significance)\cite{Sullivan2012}\cite{Thiese2016}, and cutoff. 
The effect size is the magnitude of the difference (or relationship) among comparing groups.
%A \textit{P} value is a tool to help interpret findings from biomedical research.
%In reporting and interpreting studies, both 
%the substantive significance (effect size) and statistical significance (P value) are essential results to be reported.
While statistical significance can inform the researcher whether an effect exists, 
the \textit{P} value will not directly tell the effect size.
%The effect size is the main finding of a quantitative study.
%Statistical significance depends upon both sample size and effect size. 
The effect size is independent of the sample size\cite{Sullivan2012}.

%When we increase the sample size, the standard error decrease
%, or increase the difference between the sample statistic and hypothesized parameter, the p value decreases, thus making it more likely that we reject the null hypothesis.
In a study with large sample size, the difference could be noticed easily (i.e., \textit{P} value $< 0.05$) due to a decreased standard error\cite{Sullivan2012}.
However, the small effect size (non-zero) is often meaningless or substantive insignificance.
%With a sufficiently large sample, a statistical test will always reveal a significant difference, unless the effect size is exactly zero.
%, that is, when the effect size is exactly zero; 
%yet very small differences, even if significant, are often meaningless. 
%Thus, reporting only the significant P value for an analysis is not adequate for readers to fully understand the results.
%If the magnitude of effect is small and clinically unimportant, the p-value can be "significant" if the sample size is large.
Conversely, the effect size can be significant but fail to get statistical significance if the sample size is small. 
%In this scenario, the \textit{P} value tells the effect does not exist.

The following error could also impact the \textit{P} value:
\begin{outline}
\1 A random error, defined as the variability in data, is not considered a bias but rather occurs randomly across the entire study population and can distort the measurement process (e.x. RNA-Seq experiments).
The larger sample size could reduce the random error. 
\1 A systematic error is a bias, which includes selection bias, information bias, and confounding.
It could deleteriously impact the statistical significance.
The larger sample size could not affect the systematic error.
\end{outline}
% effect size is large (whatever is true or artificial), the p value is small
Thus, if there is no error in two study groups, and the sample size is the same, the group, which has a larger effect size, will has a small \textit{P} value\cite{Thiese2016}.
If a skewed cutoff that split, for example, 425 vs. 75 between the two groups, it will also get statistical significance by increasing effect size artificially.
% https://stats.stackexchange.com/questions/162359/how-can-you-have-p-0-0001-with-a-sample-size-of-89-and-a-control-group-of-52
%As you can see, even with only 12 events (fustat = 1) that split 10 vs 2 between the two dummy groups you get a log-rank p-value < 0.0001.
%effect size, sample size, cutoff 影響 p value!

@@

%2) \\
%(ok) % pvalueTex is essential
There is a benefit for using sliding-window cutoff method (between $30\%-70\%$ quantile) in Kaplan-Meier analysis of TCGA HNSCC cohort at the beginning.
We have compared the results of cutoff at optimal \textit{P} value by sliding window or just at the median of gene expression.
It shows that the number of genes with unadjusted \textit{P} value $<0.05$, which is 6284 vs. 3118, respectively. After FDR correction, it has reduced as 967 vs. 209, respectively.
% HNSCC_OS_marginS_THREE_pvalue005_noCancerGene
%Result by optimal cutoff: total 9416 plots,
%6284 are raw KM P value < 0.05
%534?? genes are FDR KM P value <0.05
%967 genes which HR is greater than 1.5 or less than 0.5.
%Result by median cutoff: total 20080 genes, 
%3118 are raw KM P value < 0.05; 
%209 genes are FDR KM P value <0.05
The sliding-window cutoff method could catch more potential candidates, which have \textit{P} values far less than $0.001$, for subsequent Cox's modeling.
That is because of the properly selected cutoff improving the statistical significance.
Then, these preliminary candidates will have an opportunity to be carefully selected by Bonferroni correction, their effect size (HR), and the other independent cohorts (GSE65858, GSE2837) to prevent the false discovery.

@@

We will explain the above mentioned by an example.
%***NDFIP1  % 給他們一個機會
Reviewing the special case of genes, such as NDFIP1, DKC1, PNMA5, and NPB,
we have noticed that NDFIP1, with a \textit{P} value of 0.05 at 50\% quantile (median) cutoff, could achieve a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff.
NDFIP1 has the FDR-corrected \textit{P} value as \num[round-precision=3, round-mode=figures,
scientific-notation=true]{0.0001074233} (please see supplementary figure S1, a "W"-shaped \textit{P} value plot). % it is \ref{fig:pvaluePlot_NDFIP1
%Moreover, the gene NDFIP1, one of our 20 preliminary candidates, has a \textit{P} value (around $0.05$) at 50\% quantile cutoff, achieving a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff (please see Figure \ref{fig:pvaluePlot_NDFIP1}, and also in supplementary figure S1).
%After the FDR correction, NDFIP1 still has \textit{P} value of \num[round-precision=3, round-mode=figures, scientific-notation=true]{0.0001074233}.
% the effect size
Then it has been excluded as a candidate by small effect size (HR = 1.33 in GSE65858 cohort and HR = 1.42 in GSE2837 cohort) less than 1.8.
"

%compared with one (HR = 2.027) in TCGA cohort%.
% (ok) Answer 2-1 加入 discussion
%According to the results of sliding-window cutoff finding, the preliminary biomarkers have FDR-corrected \textit{P} values from \num{1e-4} to 0.04 which have been grouped by cutoffs between 50\% and 70\% quantile (Please see Figure \ref{fig:figure4}; it is also shown in manuscript as updated "Figure 4": top 3 candidate biomarkers, CAMK2N1, IL19, and FCGBP).

@@

Usually, researchers developed an in-house workflow of gene expression analysis to find HNSCC biomarkers.

@@

They have several genes that are differentially expressed between tumor and normal samples.
It would be helpful to show that alteration in gene expression correlates with phenotypes of HNSCC.

@@

The protein-protein interaction (PPI) network was conducted by STRING (available at https://string-db.org).

@@

%%%%%%%%%
\end{MyColorPar} % red
